### 2021-09-17 docs/paper/sections/1_introduction.tex
Restructure paper: extract split up approach, merge implementation

Open Source software (OSS) solutions have become more and more and important during the last decades.
Especially, this trend has been experiencing an additional updraft due to the ongoing spreading of OSS platforms such as GitHub or GitLab.
Open-source development offers many advantages as opposed to traditional closed-source development, including large numbers of volunteer contributions from the open-source community, increased transparency effects in security-related domains, and a high potential for reusing solutions.
These solutions are usually organized as \emph{packages} each of which attempts to solve an isolated problem and provide a generic interface.
Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
Other solutions or packages then can \emph{depend} on existing packages.
These dependency relations form a large directed graph that connects major parts of the software world for each popular programming language ecosystem.

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

To tackle these concerns, in this paper, we propose an approach to gather API usages from downstream dependency repositories of npm packages, in order to support package developers in surveying usages of their solutions.
We further make these data directly available to package developers by integrating them into an integrated development environment (IDE).

The rest of this paper is organized as follows:
In \cref{sec:related_work}, we give a summary of existing approaches in this field.
In \cref{sec:approach}, we outline our approach for gathering and analyzing usage data from downstream dependencies.
In \cref{sec:data_collection} and \cref{sec:usage_mining}, we describe our implementation for collecting downstream dependency repositories resp. mining usage data from these repositories.
In \cref{sec:presentation}, we sketch our design for a display of the usage data inside an IDE.
In \cref{sec:evaluation}, we examine the fitness of our data mining approach and the usability of the display solution.

>>>>

Open Source software (OSS) solutions have become more and more and important during the last decades.
Especially, this trend has been experiencing an additional updraft due to the ongoing spreading of OSS platforms such as GitHub or GitLab.
Open-source development offers many advantages as opposed to traditional closed-source development, including large numbers of volunteer contributions from the open-source community, increased transparency effects in security-related domains, and a high potential for reusing solutions.
These solutions are usually organized as \emph{packages} each of which attempts to solve an isolated problem and provide a generic interface.
Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
Other solutions or packages can then \emph{depend} on existing packages.
These dependency relations form a large directed graph that connects major parts of the software world for each popular programming language ecosystem.

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}. \TODO{do we need to prove each of this?}
Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

To tackle these concerns, in this paper, we propose an approach to extract API usage samples from downstream dependency repositories of individual packages in order to support package developers in surveying usages of their solutions.
We further make these data directly available to package developers by integrating them into an integrated development environment (IDE).

The rest of this paper is organized as follows:
In \cref{sec:related_work}, we give a summary of existing approaches in this field.
In \cref{sec:framework}, we outline the overall conditions and the general approach for our solution to mining downstream dependencies.
In \cref{sec:dependency_collection} and \cref{sec:usage_mining}, we explain our approach for collecting downstream dependency repositories resp. mining usage data from these repositories in detail.
In \cref{sec:implementation}, we describe an implementation of the proposed approach and our design decisions for displaying usage samples to the user.
In \cref{sec:evaluation}, we examine the fitness of our data mining approach and the usability of the display solution.

### 2021-09-17 docs/paper/sections/5_usage_mining.tex
Restructure paper: extract split up approach, merge implementation

\section{Usage mining}
\label{sec:usage_mining}

Foo!

>>>>

\section{Usage sample mining}
\label{sec:usage_mining}

\begin{figure*}
	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
	\newcommand\highlight[1]{\textcolor{red}{#1}}
	\centering
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/CallExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/PropertyAccessExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/JsxOpeningElement}
	\end{subfigure}

	\caption{AST patterns for example JavaScript/TypeScript expressions.
		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
	}
	\label{fig:usage_mining/patterns}
\end{figure*}
\input{sections/5_usage_mining/patterns/JsxOpeningElement.postfigure.tex}

Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.

To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.

% TODO: use term "binding"?
In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to or between a function call and the definition of this function.

In the final step, the AST is traversed again and collect all nodes that are linked to a declaration in the target package.
To identify these links, we define a set of language-specific patterns of AST subtrees that containing a declaration node (see \cref{fig:usage_mining/patterns}).

### 2021-09-17 docs/paper/sections/6_implementation.tex
Restructure paper: extract split up approach, merge implementation

\section{Approach}
\label{sec:approach}

Because of its superior popularity \TODO{prove}, in this work, we will confine ourselves to the JavaScript/npm ecosystem.
Our goal is thus to develop a tool for npm package developers that displays an overview of the downstream dependencies and their details for a chosen package.
Concretely, we pose the following key requirements to this tool:

\begin{enumerate}[label=R\arabic*]
	\item \label{req1} The tool allows package developers to survey and explore the usages of individual package members.
	\item The tool blends in well with the usual workflow of package developers.
	\item \label{req3} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
\end{enumerate}

In essence, our proposed approach to fulfill these requirements consists of three steps:
\begin{enumerate*}
	\item collect downstream dependency repositories,
	\item mine package usage samples from them,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}
In the following, we will describe each step.

\subsection{Downstream dependency collection}
\label{sec:approach/collection}

In the first step, a list of repositories that depend on the target package has to be assembled.
As mentioned in \cref{sec:related_work/usage_information}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.

As an alternative, we have decided to apply significantly stricter pre-filtering to the set of repositories before downloading it to the local machine.
For that, we have chosen two publicly available data sources:\footnote{
	Other data sources that we have rejected include GitHub code search which has limited precision results and is not freely accessible programatically as well as the \emph{libraries.io} service \citep{katz2020libraries} whose downstream dependency search was inoperative at the time of writing.%
}

\begin{enumerate}[label=(\roman*)]
	\item The npm registry which maintains a doubly-connected edge list of all npm packages that depend on each other.
	\item The code search engine \emph{Sourcegraph}\footnote{\url{https://sourcegraph.com/}} which is indexing repositories from most popular OSS platforms such as GitHub or GitLab.
		Using this search engine, we can query all repositories that declare a dependency on the target package in their package metadata file.
\end{enumerate}

Finally, we can download the source code for a small number of relevant repositories only.

\subsection{Usage sample mining}
\label{sec:approach/mining}

\begin{figure*}[htb!]
	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
	\newcommand\highlight[1]{\textcolor{red}{#1}}
	\centering
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/3_approach_assets/patterns/CallExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/3_approach_assets/patterns/PropertyAccessExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/3_approach_assets/patterns/JsxOpeningExpression}
	\end{subfigure}

	\caption{AST patterns for example JavaScript/TypeScript expressions.
		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
	}
	\label{fig:approach/mining/patterns}
\end{figure*}
\input{sections/3_approach_assets/patterns/JsxOpeningExpression.postfigure.tex}

Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.

To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.

% TODO: use term "binding"?
In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to, or between a function call and the definition of this function.

In the final step, we traverse the AST again and collect all nodes that are linked to a declaration in the target package.
To identify these links, we define a number of patterns for node structures and look up the declaration of every matched node (see \cref{fig:approach/mining/patterns}).

\subsection{Presentation of results}
\label{sec:approach/presentation}

After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
To satisfy \cref{req2} and make our tool avaiable in the usual working environment of users, we implement it as an extension to a popular IDE.
One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}.
As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.

For choosing appropriate views of the raw reference data, we have identified three common questions of package developers to answer each of which they require access to downstream dependencies and their usage samples:

\begin{enumerate}[label=Q\arabic*]
	\item Which dependencies do use the target package and what problems are they solving with it?
	\item By how many dependencies is a particular package member being used?
	\item In which contexts and constellations is a particular package member being used?
\end{enumerate}

To support developers in answering these questions and fulfill \cref{req1}, we have designed the following views for our extension:

@@

>>>>

\section{Implementation}
\label{sec:implementation}

\subsection{Data collection}
\label{sec:implementation/data_collection}

Foo!

\subsection{Usage mining}
\label{sec:implementation/usage_mining}

Foo!

\subsection{Presentation of results}
\label{sec:implementation/presentation}

After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to a popular IDE.
One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code.\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.

To support developers in answering the questions raised in \cref{sec:framework}, we have designed the following views for our extension:

@@

Foo!
